% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{Richard F. Porter\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PRESENT ADDRESS\\832 NW 10th Ave.\\Gainesville, FL 32601}
\address{\bf PERMANENT ADDRESS \\ 1210 Fairview Dr.\\Columbia, SC 29205\\(803) 487-7247}
                                  
\begin{resume}

\section{JOB OBJECTIVE}          
    A challenging software development position solving interesting problems among intelligent, experienced peers. 
 
\section{SKILLS} 
   \vspace{-0.1in}	         
 \begin{tabbing}%
   \hspace{1.2in}\= \kill
    Languages \>Python, Java, JavaScript, C, Perl, XSLT. \\
    Databases \>MySQL, SQLite, MongoDB\\
    Platforms \>Android, Linux, Web.\\    
  \end{tabbing}
  \vspace{-0.3in}	 
  
\section{EDUCATION}          
    University of South Carolina, Columbia, SC  \\        
    Masters of Engineering, Computer Science, December 2011   \\       
    \\Presbyterian College, Clinton, SC\\
    Bachelor of Arts, English Major, Math Minor, May 2007

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Python Backend Developer} \>Net Enforcers     \>Jan. 2012 -\\
                             \>Gainesville, FL\>Present
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Using Pylons 1.0, develop a Pylons backend API that pulls data from MongoDB and MySQL databases.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Developer Consultant} \>Carolina Living \>Aug. 2011 - \\
                          \>Columbia, SC\>Present
   \end{tabbing}\vspace{-20pt}
    Maintain a Classic ASP website and a custom VBScript application.  Identify new
    technologies that may add value to the business.

   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Python Developer}  \>Social and Scientific Systems \> Multiple Contracts\\
                          \>Telecommute
   \end{tabbing}\vspace{-20pt}
    Developed a custom wrapper in Python around the SAS executable to allow for 
    auditing, parameter verification, and error logging.  Created pre-/post-commit hooks
    for Subversion.  Implemented scripts to read and write a custom data format.
    
    \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Android Development Intern}  \>CTB/McGraw-Hill \> Jun. - Jul. 2011\\
                          \>Monterrey, CA
   \end{tabbing}\vspace{-20pt}
    Designed UI and class structure from project specifications.  Created an Android 
    tablet application that provided asynchronous updates.  Presented and explained
    application status and future work to exectuives.

    \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Django Developer}  \>Todayattruffles.com \> Apr. - May 2011\\
                          \>Telecommute
   \end{tabbing}\vspace{-20pt}
   Developed Django back-end to allow content editing by not-technical users.  Converted 
   mockups of pages to HTML, SASS, \& jQuery.
   
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Teacher's Assistant}  \>University of South Carolina \> Jan. 2010 - \\
                          \>Columbia, SC\>May 2011
   \end{tabbing}\vspace{-20pt}
   Explained general programming concepts as well as HTML, CSS, \& JavaScript to students in
   lab and class.  Graded students in a fair and consistent manner. 
   
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Researcher}  \>Machine Learning and Evolution Group \> Sept. 2009 - \\
                          \>Columbia, SC\>Dec. 2010
   \end{tabbing}\vspace{-20pt}
   Researched Bioinformatics techniques and algorithms.  Used Python for extraction and 
   manipulation of data.  Employed a Support Vector Machine for classification.
   
   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions          
   {\bf Intern}  \>Teradata \> Mar. - Nov. 2009\\
                          \>West Columbia, SC
   \end{tabbing}\vspace{-20pt}
   Improved existing JavaScript documentation system by adding search and fixing browser specific
   issues.  Extended the Alfresco Document Management System to add a document conversion 
   action using Java.  Enhanced existing documentation generation using XSL Transformations.

\section{HONORS AND AWARDS}          
    Eagle Scout, Boy Scouts of America \\
    Belk Scholarship, Life Scholarship \\
    \textit{Outstanding Service Project of the Year} (Dec 2005)   
       
 
\section{EXTRACURRICULAR ACTIVITIES \& LEADERSHIP POSITIONS}          
    Director of Communications (2006 - 2007), Student Volunteer Services\\
    Constitution Revision Committee (2006 - 2007), Election Committee (2007)\\
    Intern, Bluefish Campus Ministry (2006 - 2007)\\
    Volunteer, Habitat for Humanity, Clinton Child Outreach Program and CHAMPS (2006 - 2007)\\
    Contributor, Blue Stocking newspaper (2006)\\
    Senator representing Sigma Tau Delta, Student Government (2005 - 2007)\\
    Member, Sigma Tau Delta, English Honor Society (2005 - 2007)\\
    Founder, Presbyterian College Movie Television (2005 - 2007)\\
    Historian (2004 - 2005), Finance Committee Founder / Member (2005 - 2007), Webmaster (2005 - 2006), Philanthropy Chair (2007), Theta Chi Fraternity
         
 
\end{resume}
\end{document}